\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{scrextend}

%\usepackage{showframe} % debugging use only

\geometry{
  letterpaper,
  left = 0.5in,
  right = 0.5in,
  top = 0.6in,
  bottom = 0.6in
}

\hypersetup{
  colorlinks = true, 
  linkcolor = blue, 
  urlcolor  = blue,
  citecolor = blue, 
  anchorcolor = blue
}

%   CUSTOM STYLES  %
\thispagestyle{empty} % remove page number
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

%   MACROS  %
\newcommand{\sectionStart}{
  \begin{itemize}[label={},leftmargin=0in]
}
\newcommand{\sectionEnd}{
  \end{itemize}
}
\newcommand{\head}[9]{
  \noindent
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \centerline{
      \textbf{\href{#1}{\color{black}{\textbf {\underline{#2}}}}}
    }
    \vspace{5pt}\\
    \centerline{
      \href{mailto:#3}{\underline{#3}} $\mid$
      #4 $\mid$
      #5 : \href{#6}{\underline{#7}} $\mid$
      #8 : \href{#9}{\underline{#7}}
    }
  \end{tabular*}
  \vspace{-10pt}
}
\newcommand{\summaryText}[1]{
  \item
  \begin{addmargin}[7pt]{0pt}
    {#1}
  \end{addmargin}
}
\newcommand{\educationItem}[5]{
  \vspace{-1pt}
  \item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r@{}}
    {#1 in \textbf{#2}}  & {#3}\\
    {\textit{#4}} & {#5}\\\vspace{-18pt}
  \end{tabular*}
  \vspace{-5pt}
}
\newcommand{\skillItem}[2]{
  \vspace{-1pt}
  \item
  \begin{tabular*}{1.0\textwidth}{l@{}l@{}}
    {\textbf{#1}: } & {#2}
  \end{tabular*}\vspace{-17pt}
}
\newcommand{\jobHeading}[3]{
  \vspace{-1pt}
  \item
  \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r@{}}
    \normalsize{\textbf{#1}} & #2 \\
    \textit{\small#3} \\
  \end{tabular*}\vspace{-5pt}
}
\newcommand{\projectHeading}[4]{
  \vspace{-1pt}
  \item
  \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r@{}}
    \normalsize{{\href{#1}{#2}} \textbf{#3}} & #4 \\
  \end{tabular*}\vspace{-5pt}
}
\newcommand{\listStart}{\begin{itemize}}
\newcommand{\listEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\bulletItem}[1]{
  \item
  \small{
    {#1 \vspace{-1.8pt}}
  }
}

\begin{document}

%   HERO   %
\head
  {}
  {Mohamdi Veten}
  {mohamdiveten@gmail.com}
  {+90 533 240 05 22}
  {Github}
  {https://github.com/mohamdiveten}
  {mohamdiveten}
  {LinkedIn}
  {https://www.linkedin.com/in/mohamdi-veten}



 \input{includes/summary-section} %/

  
%   EXPERIENCE   %
\section{Experience}
\sectionStart
  \jobHeading
    {IT Officer}
    {May 2016 - Present}
    {SESRIC (OIC Ankara Centre), Turkey}
  \listStart
  \bulletItem
  {
Led the requirements analysis and development of an internal 
ERP using (ASP.NET/EF/MSSQL) that:
\begin{itemize}
\item  Increased the productivity of events organizers by automating participants registration, follow-up, and awarding.
\item Reduced the workload of HR by self-servicing Staff time-off requests and attendance reporting.
\item Went in production shortly and maintained stakeholders engagement via frequent, value-based delivery.  
\item Saved 70\% of the expense of off-the-shelf solution.
\end{itemize}



  }
    \bulletItem
    {Refactored a large monolithic PHP system to loosely coupled polyglot (.NET \& Python) services that intercommunicate via REST API's.}
     
    \bulletItem
    {Developed sizable collection of PowerShell \& Python scripts to automate backup, Test/Dev setup, deployment and other administrative tasks.}
    \bulletItem
    {Initiated and successfully implemented key transformative initiatives such as:  
    \begin{itemize}
    \bulletItem {Rolling out a data-driven task management and reporting system using SharePoint, PowerBI and Power Automate that helped with increasing productivity and reducing repetitive status reporting.  }
    \item Migrating codebases to Azure DevOps and configuring time-saving release/development pipelines.
    \item Upskilling and reskilling colleagues on agile methodologies and trending programming tools and practices.
    \item Fostering a culture of experimentation, open communication and focus on frequent delivery of value. 
    
    \end{itemize}
        
    }
    
    \bulletItem
    {
		Written Python ETLs to extract socioeconomic data from API's leading to: 
		\begin{itemize}
		
		\item Increased timeliness of published data by shortening the update cycle from 12 to 4 weeks.
		\item Increased speed \& quality of research by highlighting relevant metrics and data inconsistencies.
\end{itemize}		    
    }
   
    \bulletItem
    {Work closely with the Director overseeing the departmental affairs and serve as  deputy in his absence. }
    
    
    
  \listEnd
\sectionEnd


\input{includes/education-section}

%   LEADERSHIP   %
\section{Certifications}

\begin{itemize}
	\item \href{https://www.credly.com/badges/6b30cb69-ac54-4abc-b26d-61deef5c2a4c/public_url}{Microsoft Certified: Azure Data Engineer Associate}
	\item \href{https://www.credly.com/badges/36381c2d-87cc-445b-a174-b1431604a0f5/public_url}{Microsoft Certified: Azure Data Analyst Associate}
	\item \href{https://www.credly.com/badges/209afd56-075a-42e3-9ce8-88c8bc05aae5/public_url}{Microsoft Certified: Azure Data Scientist Associate}
	\item \href{https://www.credly.com/badges/1d886867-8f7b-45d5-b2ee-5416127e3d36/public_url}{Microsoft Certified: Azure Fundamentals}
\end{itemize}

\input{includes/techskills-section}


\end{document}