\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{scrextend}

%\usepackage{showframe} % debugging use only

\geometry{
  letterpaper,
  left = 0.5in,
  right = 0.5in,
  top = 0.6in,
  bottom = 0.6in
}

\hypersetup{
  colorlinks = true, 
  linkcolor = blue, 
  urlcolor  = blue,
  citecolor = blue, 
  anchorcolor = blue
}

%   CUSTOM STYLES  %
\thispagestyle{empty} % remove page number
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

%   MACROS  %
\newcommand{\sectionStart}{
  \begin{itemize}[label={},leftmargin=0in]
}
\newcommand{\sectionEnd}{
  \end{itemize}
}
\newcommand{\head}[9]{
  \noindent
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \centerline{
      \textbf{\href{#1}{\color{black}{\LARGE {\underline{#2}}}}}
    }
    \vspace{5pt}\\
    \centerline{
      \href{mailto:#3}{\underline{#3}} $\mid$
      #4 $\mid$
      #5 : \href{#6}{\underline{#7}} $\mid$
      #8 : \href{#9}{\underline{#7}}
    }
  \end{tabular*}
  \vspace{-10pt}
}
\newcommand{\summaryText}[1]{
  \item
  \begin{addmargin}[7pt]{0pt}
    {#1}
  \end{addmargin}
}
\newcommand{\educationItem}[5]{
  \vspace{-1pt}
  \item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r@{}}
    {#1 in \textbf{#2}}  & {#3}\\
    {\textit{#4}} & {#5}\\\vspace{-18pt}
  \end{tabular*}
  \vspace{-5pt}
}
\newcommand{\skillItem}[2]{
  \vspace{-1pt}
  \item
  \begin{tabular*}{1.0\textwidth}{l@{}l@{}}
    {\textbf{#1}: } & {#2}
  \end{tabular*}\vspace{-17pt}
}
\newcommand{\jobHeading}[3]{
  \vspace{-1pt}
  \item
  \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r@{}}
    \normalsize{\textbf{#1}} & #2 \\
    \textit{\small#3} \\
  \end{tabular*}\vspace{-5pt}
}
\newcommand{\projectHeading}[4]{
  \vspace{-1pt}
  \item
  \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r@{}}
    \normalsize{{\href{#1}{#2}} \textbf{#3}} & #4 \\
  \end{tabular*}\vspace{-5pt}
}
\newcommand{\listStart}{\begin{itemize}}
\newcommand{\listEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\bulletItem}[1]{
  \item
  \small{
    {#1 \vspace{-1.8pt}}
  }
}

\begin{document}

%   HERO   %
\head
  {}
  {Mohamdi Veten}
  {mohamdiveten@gmail.com}
  {+90 533 240 05 22}
  {Github}
  {https://github.com/mohamdiveten}
  {mohamdiveten}
  {LinkedIn}
  {https://www.linkedin.com/in/mohamdi-veten}

\input{summary}

%   EXPERIENCE   %
\section{Experience}
\sectionStart
  \jobHeading
    {IT Officer}
    {May 2016 - Present}
    {SESRIC (OIC Ankara Centre), Turkey}
  \listStart
  
  \bulletItem{
Self initiated and led the migration of  IT and data estate to the cloud (Azure and Office 365), first of its kind among the Centre's subsidiary peers.

 \bulletItem
    {Led and successfully implemented additional key transformative initiatives such as:  
    \begin{itemize}
    \item Rolling out a data-driven task management and reporting system using SharePoint, PowerBI and Power Automate that helped with increasing productivity and reducing repetitive status reporting.
    \item Migrating codebases to Azure DevOps and configuring time-saving release/development pipelines.
    \item Upskilling and reskilling colleagues on agile methodologies and trending tools and practices.
    \item Fostering a culture of experimentation, open communication, and focus on frequent delivery of value. 
    \end{itemize}
        
    }
    
  
  }
  
   \bulletItem
    {Developed sizable collection of PowerShell \& Python scripts to automate backup, Test/Dev setup, deployment and other administrative tasks.}
   
  \bulletItem
  {
Collaborated with 3 developers to develop a system using (ASP.NET/EF/MSSQL) that:
\begin{itemize}
\item  Increased the productivity of events organizers by automating clients registration, follow-up, and awarding.
\item Reduced the workload of HR by self-servicing time-off requests and attendance reporting.
\item Saved 70\% of the expense of off-the-shelf solution.
\item Concluded weeks earlier than scheduled by engaging stakeholders and negotiating non-value-add requirements.  
\end{itemize}

  }
 
 \bulletItem
 {
 Organized training series to staff on Microsoft Project, SharePoint, and Office 365 which fostered inter-departmental collaboration and helped put realizable estimates.
 }
  
    \bulletItem
    {Work closely with the Director overseeing the departmental affairs and serve as  deputy in his absence. }
  \listEnd
  
  
  
\sectionEnd

\input{../includes/certifications}


\input{../includes/education}


\input{skills}
  
  
 
\end{document}